\verse{For to find Mad Tom of Bedlam, ten thousand miles I'd travel,
Mad Maudlin goes on dirty toes for to save her shoes from gravel.}

\chorus{Still I sing bonny boys, bonny mad boys, Bedlam boys are bonny,
For they all go bare and they live by the air and they want no drink nor money.}

\verse{I now repent that ever Mad Tom was so disdainèd,
My wits were lost since him I crossed - it makes me thus go chainèd.}

\verse{I went to Satan's Kitchen to beg some food one morning,
And there I got souls piping hot, all on the spit a-turning.}

\verse{I there picked up a cauldron where boiled ten thousand harlots,
Though full of flame, I drank the same to the health of all such varlets.}

\verse{My staff has murdered giants, my bag a long knife carries,
For to cut mince pies from children's thighs, with which to feed the fairies.}

\verse{The spirits white as lightning will on my travels guide me,
The stars would shake and the moon would quake whenever they espied me.}

\verse{No gypsy, slut, or doxy shall win my Mad Tom from me.
I’ll drink all night, with the stars I’ll fight; the fray shall well become me.}

\verse{And when that I have murdered the man in the moon to powder,
His staff I'll break and his dog I'll take, then howl no demon louder.}

\verse{A spirit hot as lightning did on that journey guide me.
The stars did shake and the pale moon quake as soon as ere they spied me.}

\verse{So drink to Tom o' Bedlam, go fill the seas in barrels.
I'll drink it all, well brewed with gall, and maudlin drunk I'll quarrel.}