\verse{When I was a young man, I carried me pack,
And I lived the free life of the rover.
From the Murray's green basin to the dusty outback,
I waltzed my Matilda all over.
Then in nineteen fifteen my country said ``Son,
It's time to stop rambling, there's work to be done".
So they gave me a tin hat and they gave me a gun,
And they sent me away to the war.
And the band played Waltzing Matilda
As the ship pulled away from the quay,
But amidst all the cheers, the flag-waving and tears,
We sailed off for Gallipoli.}

\verse{How well I remember that terrible day,
How blood-stained the sand and the water,
And how in that hell that they called Suvla Bay
We were butchered like lambs at the slaughter.
Johnny Turk, he was ready, he'd primed himself well,
He chased us with bullets, he rained us with shell,
And in five minutes flat, he'd blown us all to hell,
Nearly blew us right back to Australia.
But the band played Waltzing Matilda
When we stopped to bury our slain.
We buried ours, and the Turks buried theirs,
Then we started all over again.}

\verse{Now those that were left, well we tried to survive
In a mad world of blood, death and fire,
And for ten weary weeks, I kept myself alive,
Though around me the corpses piled higher.
Then a big Turkish shell knocked me arse over head
And when I woke up in my hospital bed
I saw what it had done, and I wished I was dead.
Never knew there was worse things than dyin'.
For I'll go no more waltzing Matilda
All around the green bush far and near.
For to hump tent and pegs, a man needs both legs
No more waltzing Matilda for me.}

\verse{So they collected the crippled, the wounded and maimed,
And they shipped us back home to Australia:
The legless, the armless, the blind and insane,
Those proud wounded heroes of Suvla.
And as our ship pulled into Circular Quay,
I looked at the place where me legs used to be
And thanked Christ there was no-one there waiting for me
To grieve and to mourn and to pity.
But the band played Waltzing Matilda
As they carried us down the gangway.
But nobody cheered, they just stood and stared,
Then they turned all their faces away.}

\verse{So now every April, I sit on my porch,
And I watch the parade pass before me,
And I see my old comrades, how proudly they march,
Renewing old dreams and past glory.
And the old men march slowly, all bent, stiff and sore,
The tired old heroes from a forgotten war,
And the young people ask, ``What are they marching for?",
And I ask myself the same question.
But the band plays Waltzing Matilda,
And the old men still answer the call,
But year by year, their numbers get fewer,
Someday no one will march there at all.}

\verse{Waltzing Matilda, Waltzing Matilda,
Who'll come a-waltzing Matilda with me?
And their ghosts may be heard
As they pass by that billabong,
Who'll come a-waltzing Matilda with me?}