\verse{There once was a boy from the forest, as pale as any milk,
His hair was like the strands of gold, his skin soft as the silk.}

\verse{He liked to walk in the forest, lamenting to the air,
For everyone he knew would say no boy could be so fair.}

\verse{It started from his birth when the midwife was heard to say
``Oh, rejoice, you happy parents for a girl is born today."}

\verse{And as this child grew older, it grated on his soul
That those who met him, every one, said ``Hey now, little girl."}

\verse{One day in the month of May, the rain was pouring down,
It helped to wash his salty tears and hide away his frown.}

\verse{He was walking all alone, his thoughts were turning grey
When a voice called to him oh so clear, ``What brings you here this way?"}

\verse{``Oh, I am a boy from the forest, this path I know so well.
Perhaps it is I who should ask you since when did you here dwell?"}

\verse{The voice came closer to him and whispered in his ear,
``Oh, boy I’ve watched you come this way and your grief did overhear."}

\verse{The boy he turned so slowly to see what was at his back
And he looked into the shining eyes of a cat that was so black.}

\verse{``Yes, boy, your eyes don’t deceive you, this is indeed my form.
It’s a little-known fact that cats like me are the spirits of the storm."}

\verse{``Sit down, my boy," he said. ``Some sympathy you’ve earned,
A boy you came into the forest, a man you will return."}

\verse{The boy sat on a log, the cat, his path now cleared,
Curled his tail round the face of the forest boy to form a black-haired beard.}

\verse{``No more will they think you a girl," said the cat with a grin,
And as he vanished into air the boy saw a stump where his tail had been.}

\verse{And so the boy became a man, the people they cried witch,
Not only had he grown a beard, but it was black as pitch.}

\verse{No more the boy from the forest, he wandered far and wide 
Til at last even strangers knew him for the man he was inside.}

\verse{There once was a man from the forest, as pale as any milk,
His hair was like the strands of gold, his skin soft as the silk.}

\verse{And his beard was black as night, his fame it spread and ran
Across the seas till everyone knew of the island of the man.}

\verse{If ever you visit the island and see a tailless cat walk past,
Remember the boy from the forest and how he became a man at last.}
