\verse{A man cam' riding oot the west one wild and stormy day,
He was tall, quiet, and hungry, his eyes were smokey grey.
He was lean across the hurdies, but his shoulders they were big.
The terror o' the hielan' glens, that was the Portree Kid.}

\verse{His sidekick was an orra'man, and oh but he was mean,
He was called the Midnight Ploughboy, and he cam' frae Aberdeen.
He had twenty-seven notches in his cromack so they say,
And he killed a million Indians way up in Stornaway.}

\chorus{He drum ho, he drum hey,
The teuchter that cam' frae Skye.}

\verse{Portee booted in the door, he sauntered tae the bar,
He poured a shot of Crabbies, he shouted Sl\`{a}inte Mhath,
While Midnight was being chatted up by a bar room girl called Pam
Who said ``Well howdy stranger, wad' ye buy's a Babycham?"}

\verse{Now over in the corner sat three men frae Auchtertool
They were playing games for money, in a snakes and ladders school.
The fourth man was a southerner who'd come up from Macmerry,
He'd been a river gambler on the Ballachulish Ferry.}

\verse{Portree walked tae the table and he shouted ``Shake me in!",
He shoogled on the eggcup, he gave the dice a spin.
He threw seven sixes in a row, the game was nearly done,
But then he landed on a snake, and finished on square one.}

\verse{The game was nearly over and Portree was doing fine.
He'd landed on a ladder, he was up to forty nine.
He only had but one to go and the other man was beat,
But the gambler cowped the board up and shouted ``You're a cheat!"}

\verse{Men dived behind their rubber plants to try and save their skins,
The accordionist stopped playing, his sidekick dropped the spoons.
He says ``I think it's funny, you've been up that ladder twice,
And ye ayeways dunt the table when I go tae throw my dice."}

\verse{The gambler drew his Sgian-Dubh as fast as lightning speed,
Portree grabbed a screwtop, he cracked him o'er the heid,
Then he gave him laldy wi' a salmon off the wall,
And he finished off the business wi' his lucky grousefoot's claw.}

\verse{Portree walked up tae the bar, he says ``I'll hae a half
And d'ye like the way I stuck it on that wee Macmerry nyaff?"
But the southerner crept up behind, his features wracked with pain,
And he gubbed him wi' an ashtray made oot o' a curling stane.}

\verse{The fight went raging on all night till opening time next day,
Wi' a break for soup and stovies aff a coronation tray.
It was getting kind of obvious that neither man would win
When came the shout that stopped it all: ``There's a bus trip coming in!"}

\verse{They sing this song in Galashiels and up by Peterheid,
Way down o'er the border and across the Rio Tweed,
About what became o' Portree, Midnight, and the Gambling Man:
They opened up a gift shop selling fresh air in a can.}
